\pdfminorversion=7
\documentclass[sigconf,10pt,noacm]{acmart}
\usepackage{geometry}
\geometry{reset, twoside=true, head=13pt,
     paperwidth=8.5in, paperheight=11in,
     includeheadfoot, columnsep=2pc,
     top=57pt, bottom=73pt, inner=72pt, outer=72pt,
     marginparwidth=2pc,heightrounded
     }

\usepackage[utf8]{inputenc}
%\usepackage{fontspec} % This line only for XeLaTeX and LuaLaTeX
\usepackage{pgfplots}
\pgfplotsset{compat=1.16}
\usepackage{tikz}


\usepackage{booktabs} % For formal tables
\usepackage{balance}       % to better equalize the last page
% Load basic packages
\usepackage{balance}       % to better equalize the last page
%\usepackage{graphics}      % for EPS, load graphicx instead 
\usepackage{graphicx}
%\usepackage[T1]{fontenc}   % for umlauts and other diaeresis
%\usepackage{txfonts}
%\usepackage{mathptmx}
%\usepackage[pdflang={en-US}]{hyperref}
\usepackage{hyperref}
%\usepackage{color}
\usepackage{textcomp}
\usepackage{blindtext}
\usepackage{subcaption}
\usepackage{dblfloatfix}
\usepackage{adjustbox}

\usepackage{booktabs}
\usepackage{multirow}
% \usepackage{lscape}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\usepackage{siunitx}
%\usepackage{pgfplotstable}
% Some optional stuff you might like/need.
\usepackage{microtype}        % Improved Tracking and Kerning
\usepackage[all]{hypcap}    % Fixes bug in hyperref caption linking
\usepackage{ccicons}          % Cite your images correctly!
% \usepackage[utf8]{inputenc} % for a UTF8 editor only

% If you want to use todo notes, marginpars etc. during creation of
% your draft document, you have to enable the "chi_draft" option for
% the document class. To do this, change the very first line to:
% "\documentclass[chi_draft]{sigchi}". You can then place todo notes
% by using the "\todo{...}"  command. Make sure to disable the draft
% option again before submitting your final document.
%\usepackage{todonotes}
%\usepackage{draftwatermark}
%\SetWatermarkScale{5}

\usepackage{graphicx}
\usepackage{type1cm}
\usepackage{eso-pic}
\usepackage{lipsum}

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.

% Copyright
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


%\copyrightyear{2019} 
%\acmYear{2019} 
%\setcopyright{rightsretained}
%\acmConference[HotOS XVII]{The 17th Workshop on Hot Topics in Operating Systems (HOTOS)}{May 12-15, 2019}{Bertinoro, Italy}
%\acmBooktitle{Proceedings of the 17th Workshop on Hot Topics in Operating Systems (HOTOS '19), May 12-15, 2019, Bertinoro, Italy}
%\acmPrice{15.00}
%\acmDOI{10.475/123_4}
%\acmISBN{123-4567-24-567/08/06}
\acmConference{}
\acmBooktitle{}
\acmPrice{}
\acmDOI{}
\acmISBN{}
\acmYear{}

% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
%\editor{Jennifer B. Sartor}
%\editor{Theo D'Hondt}
%\editor{Wolfgang De Meuter}

\pagestyle{plain}
\settopmatter{printacmref=false}
%\settopmatter{printfolios=false}
%\setlength {\marginparwidth}{2cm}
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column

\setlength{\textfloatsep}{10pt plus 1.0pt minus 2.0pt}
\setlength{\intextsep}{6pt plus 2.0pt minus 2.0pt}

\begin{document}
\title{Not Dead Yet}
\subtitle{Hierarchical File Systems Won't Die}

\author{Tony Mason}
\orcid{0000-0002-0651-5019}
\affiliation{%
  \institution{The University of British Columbia}
}
\email{fsgeek@cs.ubc.ca}

\author{Margo Seltzer}
\affiliation{%
\institution{The University of British Columbia}
%\city{Atlanta}
%\state{Georgia}
%\country{US}
}
\email{mseltzer@cs.ubc.ca}

% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{T. Mason et al.}

%
% Generated this code.  Should review it
%
\begin{comment}
\begin{CCSXML}
  <ccs2012>
  <concept>
  <concept_id>10003456.10003457.10003527.10003531.10003533</concept_id>
  <concept_desc>Social and professional topics~Computer science education</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  <concept>
  <concept_id>10003456.10003457.10003527.10003531.10003533.10011595</concept_id>
  <concept_desc>Social and professional topics~CS1</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  <concept>
  <concept_id>10003456.10003457.10003527.10003540</concept_id>
  <concept_desc>Social and professional topics~Student assessment</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  </ccs2012>
  
\end{CCSXML}

\ccsdesc[300]{Social and professional topics~Computer science education}
\ccsdesc[300]{Social and professional topics~CS1}
\ccsdesc[300]{Social and professional topics~Student assessment}
\end{comment}

\begin{comment}
\keywords{Graph File System}
\end{comment}

\makeatletter
\def\@copyrightspace{\relax}
\makeatother

\maketitle

\balance

\input{macros}

\input{abstract.tex}

\begin{comment}
  Margo comments from our January 11 meeting.

  Introduction: we have hieararchy but we need graph storage.  We see this as far back as Multics, where they have hard links,
  and UNIX, where they add symlinks [though I don't think symlinks showed up in 1974, but they did eventually.]

  The goal was to mirror the physical world of how filing systems worked [cabinets, drawers, folders, documents.  But this
  ignores the fact that libraries add cross-references - a separate name space of indices that help us find things.  And
  how documents refer to other documents, creating a "web of references".  This is not a new observation and includes
  memex and intelligent document editing systems.]

  Look at storage versus namespace: how tightly coupled are they?
  Paradigm shift: the web started with a more hierarchical model but moved to a graph model.  It also introduced
  the search based metaphor. As the web has grown, this perspective has permeated all of data storage, as we
  can see by the rampant popularity of key-value stores, object caches, etc.

  Namespace

  * Ignored by most users
  * Evolved from the web perspective
  * Those of us in "the field" still fall back to brute force search with find and grep -R

  File systems search and web search have merged into things like Dropbox, Google Drive, One Drive, and Git.

  "One author spent 20 minutes trying to find a document trying to find data from the previous work.  Had to
  search computer, Google Drive, dropbox, various repositories, etc."  Ultimately found that the data wasn't
  in any of those places and managed to get it from a co-author.

  Question: is this a systems problem or an HCI problem?

  Systems problem: data objects related via an extensible set of complex relationships that the system does
  nothing to facilitate.

  This suggests a graph structure.  Our current data storage and name space layers do not support this well.

  The HCI aspect of this is how to exploit a richer structure, so now we have a chicken and egg problem. Thus,
  we ask the question: "how should we rethink the file system to permit capturing a richer set of relationships?

  Alternatives become Background
    * Semantic file systems
    * Tagging (old, manual)
    * Tagging (new, automated/AI driven)
    * Databases

  We argue that it requires a custom, specialized database for our domain problem (e.g., relationship enhanced
  file systems).

  Limit BG to one page.

  ** maybe put Alternatives/Background AFTER our proposal ***

  Our proposal should be ~ 2 pages.

    * Envision your file system as a social graph for this discussion - a "social network file system"
    * Characteristics of data (what something "is") - one kind of relationship.
    * Social network: has people, groups, organizations)
    * File system: blob store, chunks of data
    * Shared "attributes" are one form of relationship (mapping social network to file system)
    
    What does the facebook architecture look like?  A SQL database (MySQL) with a cache (Tau)

    Why not use this as our architecture?  The analogy is not perfect.  Objects have a fixed schema in
    the database world but files do not.  Files vary in all sorts of ways and typically have an internal
    (private) schema.  They have a potentially broader range of attributes, though often we embed these
    in the name now (extension).  File systems typically store sizes, dates, and lengths.  Thus, we argue
    that we already have a partially mapped schema, but it is a rigid one.

    Proposed architecture:
      * storage - this is SOLVED for our purposes, regardless of whether the storage layer is a traditional
        HFS, a blob store, a document database, local or remote to the device.

      * relationships -
        - how do we store them?
        - how do we represent them?
        - how do we process them?

        PRESENTATION of these to users is an HCI problem.
        IMPLEMENTATION of these features is a systems problem.

    Q: why not a graph database?  Observation: in fact, we're a user of the graph database, but we aren't
       a graph database for the same reason a file system isn't a relational database: our needs are more
       simpler, so we can focus on optimizing performance for our use cases.

       Our blobs (files) are potentially quite large.
       Our relationships are ...

  Need to include the Burrito (Guo) reference.  Margo thought he had a more recent paper as well in the area,
  I need to look.

  Note: provenance is one type of relationship.

  We need a table of relationships.  This is demonstrative, not definitive.

  How do we achieve metadata efficiency?  Clustering?  Storage locality and clustering?

  Review: Plan 9, which had per-user and per-process namespaces.

  We must be able to uniquely identify a file [need to define uniquely identify].

  A "re-find" with a nice API

  A cache of recent files.

  Names may be ephemeral, since users cannot remember that much.

  Build our model from here.

  We could add a container on top that elevates this relationship above all others - the hierarchical model.

  Concrete proposal for graph FS.

\end{comment}

\input{intro.tex}

\input{graph.tex}

\input{search.tex}

\input{alternatives.tex}

\input{conclusion.tex}

%\input{notes.tex}

\clearpage
\pagebreak

% I add a table of nocites here to get a list of all the papers in the bibtex
% comment out to only use the references in the paper itself.
\begin{comment}
\nocite{daley1965general}
\nocite{koetsier2013digg}
\nocite{ritchie1973unix}
\nocite{wilkes1964programmer}
\nocite{reinsel2018data}
\nocite{macdonald1956datafile}
\nocite{halasz1982analogy}
\nocite{shapiro1964extracting}
\nocite{microsoft:data-add-in}
\nocite{apple:spotlight-extensions}
\nocite{chou2015findfs}
\nocite{vicente1988accommodating}
\nocite{marsden2003improving}
\nocite{jones2005don}
\nocite{karger2006data}
\nocite{ma2009file}
\nocite{jensen2010life}
\nocite{karlson2011version}
\nocite{odom2012lost}
\nocite{Thereska2013}
\nocite{harper2013file}
\nocite{mendez2012linked}
\nocite{bothorel2015clustering}
\nocite{huo2016mbfs}
\nocite{jayalakshmi2016semantic}
\nocite{carvalho2016finding}
\nocite{gao2016implicit}
\nocite{hua2016real}
\nocite{di2017gfs}
\nocite{lindley2018exploring}
\nocite{khan2018forgotten}
\nocite{vitale2018hoarding}
\nocite{laursen2014}
\nocite{boardman2003too}
\nocite{nayuki2017}
\nocite{martin2004formal}
\nocite{martin2008}
\nocite{martin2014}
\nocite{soules2004toward}
\nocite{gifford1991semantic}
\nocite{corbato1965introduction}
\nocite{Faubel2008}
\nocite{harlan2011joinfs}
\nocite{Jan2011}
\nocite{Soules2004}
\nocite{Suguna2015}
\nocite{Andrews2012}
\nocite{Eck2011}
\nocite{Hua2010}
\nocite{Joshi}
\nocite{Mander1992}
\nocite{Martin2004}
\nocite{ngo2007integrating}
\nocite{Omvlee2009}
\nocite{wang2003managing}
\nocite{Seltzer2009}
\nocite{Shah2007}
\nocite{Up2016}
\nocite{gopal1999integrating}
\nocite{Martin2005}
\nocite{Reiser2016Name}
\nocite{Benefits2016}
\nocite{Codocedo2015}
\nocite{Ghemawat2003}
\nocite{Jones2016}
\nocite{Mahalingam2003}
\nocite{Os2016}
\nocite{Parker-Wood2014}
\nocite{Prabhakaran2005}
\nocite{Schandl2009}
\nocite{cellier2008formal}
\nocite{strong2013semantic}
\nocite{Xu2014}
\nocite{olson1993design}
\nocite{Leung2009}
\nocite{Schandl2009a}
\nocite{Shah2006}
\nocite{Wiki2016}
\nocite{vicente1987assaying}
\nocite{malone1983people}
\nocite{terrizzano2015data}
\nocite{watson2017exploring}
\nocite{mogul1986representing}
\nocite{GuoBurrito2012}
\nocite{macko2015llama}
\nocite{margo2015scalable}
\nocite{macko2013performance}
\nocite{aws:s3:object:tagging}
\nocite{balabine1999file}
\nocite{stonebraker1994mariposa}
\nocite{balabine2002database}
\nocite{xu2003towards}
\nocite{kashyap2004file}
\nocite{ames2006lifs}
\nocite{koren2007searching}
\nocite{huang2012just}
\nocite{xu2009semantic}
\nocite{murphy2002design}
\nocite{leung2009magellan}
\nocite{frieder2012hierarchical}
\nocite{bush1945we}
\nocite{whang1991multilevel}
\nocite{kumar1997browsing}
\nocite{van2003beamtrees}
\nocite{dumais2016stuff}
\nocite{soules2003can}
\nocite{maccormick2004boxwood}
\nocite{marchionini2006exploratory}
\nocite{brandt2009fusing}
\nocite{leung2009spyglass}
\nocite{ren2013tablefs}
\nocite{niazi2017hopsfs}
\nocite{van2011efficient}
\nocite{215e74710c2245a59b2ce117f9e74cd7}
\nocite{appuswamy2014building}
\nocite{Harlan2011}
\nocite{Min2015}
\nocite{Open2016}
%\nocite{SemFS2016}
\nocite{Chou2015}
\nocite{Ngo2015}
%\nocite{Regatta2016}
\nocite{Gopal}
\nocite{Beydoun2009}
\nocite{Gifford2006}
\nocite{Hyvonen2004}
\nocite{Siekmann}
\nocite{Strong}
%\nocite{Dantalian2016}
\nocite{Escriva2015}
\nocite{Agee2016}
\nocite{Gifford1991}
\nocite{Guide2016}
\nocite{Liu2006}
\nocite{needham1977cap}
\nocite{arenas2016faceted}
\nocite{tunkelang2009faceted}
\nocite{hearst2006design}
\nocite{arenas2016faceted}
\nocite{klungre2018evaluating}
\nocite{walton2015searching}
\nocite{walton2017looking}
\nocite{cleverley2015retrieving}
\nocite{huurdeman2016active}
\end{comment}

\bibliographystyle{IEEEtranSN}
\bibliography{notdead} 

\end{document}
